\section{Conclusion}
\label{sec:conc}

%Conclusions (don't summarize your work here. That's what the abstract
%was for. Instead provide some philosophical ruminations of your work and
%future possibilities, i.e., conclusions that you have arrived at as a
%result of your work.)

This project explored developing and evaluating experiments that sought out to find potential vulnerabilities within a set of Android apps. 
After downloading the apps, we then developed a set of five experiments to cover three domains: permission misuse, SSL API misue, and interface vulnerabilites.

Our work shows the importance of understanding the permissions that an app requests along with their implications to be used or used together potentially maliciously by attackers. 
Another factor is the importance of understanding the SSL API calls that an app makes. Communicating securely over the internet with the use of SSL is vital to the privacy and security 
of users data and personal information. Our tool developed in this project showcases the implications of scanning Android applications for potential vulnerabilities before entering or while in the market, 
or to catch in the early stages of development. Tools like this could help aid developers and security professionals alike. 
\bigskip
\newline
\textbf{Main takeaways include}:
\begin{enumerate}
    \item Static analysis is a powerful baseline in order to target specific sectors within an app in order to identify potential vulnerabilities and attack vectors.
    \item This project's result signifies the importance of best security practices when developing and publishing Android applications.
    \item The graphs and tables help to visulize the data and results to see trends and potentially repeated bad practices and vulnerabilities. 
\end{enumerate}

Overall, this project serves as a stepping stone for an ever growing field of work. With mobile phone technology improving each year, the need for secure applications is more important than ever.
Tools like CRAB-Droid can quickly and effectively aid developers and security professionals to identify potential vulnerabilities within applications and minimize the threats awaiting their users.
